Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research

### 2023-12-10 manuscript/paper.Rmd
update

```{r source-file, echo=FALSE, include=FALSE}
# source file 
source(file = "C:/Users/monic/OneDrive/Desktop/SleepBP/data/scrip2.R")
```

@@

Our current analyses combine the 2015 - 2018 NHANES survey cycles to
yield $n = 19225$ observations on 35 covariates. This sample size was
comprised $n = 9971$ and $n = 9254$ observations from the 2015/2016 and
2017/2018 survey cycles, respectively. Analyses excluded individuals
with missing data on sleep ($n = 6818$), blood pressure (BP) (n = 1055),
and body mass index (BMI) or those with BMI \> 25 kg/$m^2$ (overweight)
(n = 5521). Individuals that reported being on anti-hypertensive
medication were also excluded from further analyses (n = 2944).

@@

### Exposure:

Sleep duration on workdays was evaluated by the questionnaire with the
following questions: "Number of hours usually sleep on weekdays or
workdays". Sleep duration was divided into three groups, which were \< 6
h, 6--8 h, ≥ 8 h respectively, of which 6--8 h was used as the reference
group.

>>>>

```{r source-file, echo=FALSE, include=FALSE}
# source file 
source(file = "../SleepBP/data/scrip2.R")
```

@@

Our current analyses combine the 2015 - 2018 NHANES survey cycles to
yield $n = 19225$ observations on 35 covariates. This sample size was
comprised $n = 9971$ and $n = 9254$ observations from the 2015/2016 and
2017/2018 survey cycles, respectively. Analyses excluded individuals
with missing data on sleep ($n = 6818$), blood pressure (BP) (n = 1055),
and body mass index (BMI) or those with BMI \> 25 kg/$m^2$ (overweight)
(n = 5521). Individuals that reported being on anti-hypertensive
medication were also excluded from further analyses (n = 2944). Our final analyses were based on a sample of n = 1977 observations on 28 covariates.

@@

### Exposures:

Sleep duration on workdays was evaluated by the questionnaire with the
following questions: "Number of hours usually sleep on weekdays or
workdays". We then categorized this variable into three groups, that is, \< 6
h, 6--8 h, ≥ 8 h respectively, and used < 6 h as the reference
group in our analysis. We also explored the association between total cholestrol (in mmol/L) level on systolic blood pressure including potential effect modification by other factors.
